# Client Survey

:::{.callout-note}
## #TODO

- Add condensed summarise of satisfaction / reflection indicators
- Experiment with dimensionality reduction techniques to distill variatoin in satisfaction / reflection indicators
:::

```{r xp-client-setup}
#| warn: false
#| message: false
#| echo: false
library(tidyverse)
library(labelled)
library(gt)
library(reactable)
library(sparkline)
library(bptheme)
library(bpscales)
source(here::here("R/zzz.R"))
source(here::here("R/extract.R"))
source(here::here("R/transform.R"))

d0 <- load_qx_surveys()
d <- d0 |> clean_client(bot_threshold = 1)
labs <- d |> var_label()

d_long_raw <- d |>
    mutate(
        across(matches("reached$"), ~ .x == "Yes"),
        engage_reached = eng_received_es != "I have never received employment services"
    ) |>
    pivot_longer(
        matches("^ig_"),
        names_to = "inclusion_group",
        values_to = "ig_member"
    ) |>
    filter(
        !is.na(ig_member)
    ) |>
    mutate(
        inclusion_group_label = unlist(labs[inclusion_group]), 
        ig_short = str_extract(inclusion_group_label, "^\\[.*\\]")
    )

d_long <- d_long_raw |>
    filter(ig_member) |>
    select(-ig_member)
```

## Preliminary Notes

:::{.callout-warning}
## Data Quality Issues

We observe some suspicious patterns in the data that are currently pending a more detailed investigation. 
These findings should be taken with more grains of salt than advised in the section introduction. 
:::

- What we see in the data is a broad pattern of low satisfaction with employment services
- If we take the responses at face value, they paint a picture of a system that troubling portions of its clients neither understand, feel understood by, trust, nor find effective
- At a glance, we see that newcomers, youth, and Indigenous clients have particularly less positive experiences 

## Respondent Characteristics

### Inclusion Group Representation

@tbl-xp-client-ig-rep shows the representation of inclusion groups among client survey respondents. 

```{r xp-igo-client-survey}
#| label: tbl-xp-client-ig-rep
#| tbl-cap: "Inclusion Group Representation in Client Survey"
#| warning: false
dplt_client_ig <- d_long_raw |> 
    group_by(inclusion_group_label) |>
    summarize(
        N = n(),
        n = sum(ig_member),
        p = n / N
    ) |>
    mutate(
        pn = glue::glue("{scales::percent(p, accuracy = 1)} ({n}/{N})")
    ) |>
    arrange(desc(p)) 

dplt_client_ig |>
    select(inclusion_group_label, sample_representation = pn) |>
    arrange(inclusion_group_label) |> 
    gt() |>
    gtExtras::gt_theme_538() |>
    tab_source_note(
        source_note = dl_button(dplt_client_ig, "xp-client-igo")
    )
```

@fig-xp-client-intersections shows the representation of each pair of inclusion groups among client survey respondents. Pairwise, the most common intersections we see are racialized newcomers, newcomers receiving social assistance, racialized francopohones, and francophone newcomers. 

```{r}
#| label: fig-xp-client-intersections
#| fig-cap: "Inclusion Group Intersections in Client Survey"
dplt_ig_int <- d_long_raw |> 
    filter(ig_short != "[Z]") |> 
    select(response_id, ig_x = ig_short, val_x = ig_member) |> 
    filter(!is.na(val_x)) %>%
    left_join(
        rename(., ig_y = ig_x, val_y = val_x),
        by = "response_id",
        relationship = "many-to-many"
    ) |>
    group_by(ig_x, ig_y) |>
    summarize(
        N = n(),
        n = sum(val_x * val_y),
        p = mean(val_x * val_y)
    )

dplt_ig_int |>
    ggplot(aes(ig_x, ig_y, fill = p)) +
    geom_tile() +
    geom_label(aes(label = scales::percent(p, accuracy = 1)), color = "black", fill = "grey90", size = 10) +
    scale_fill_viridis_c() +
    theme_blueprint(base_size = 14)

```

### Demographics

@tbl-key-demos summarizes gender, parenthood, and age: the demographic characteristics included in the client survey but not reflected in the inclusion group indicator variables. 

```{r}
#| label: tbl-key-demos
#| tbl-cap: "Age Distribution of Client Survey Respondents by Inclusion Group"
tbl_key_demos <- d_long |> 
    group_by(inclusion_group_label) |>
    summarize(
        p_woman_plus = mean(demo_gender != "Man", na.rm = TRUE),
        p_parent = mean(demo_parent, na.rm = TRUE),
        mean_age = mean(demo_age, na.rm = TRUE),
        age_dist = list(demo_age),
    )

reactable(
    tbl_key_demos,
    columns = list(
        p_woman_plus = colDef(
            cell = function(value) {
                scales::percent(value, accuracy = 1)
            }
        ),
        p_parent = colDef(
            cell = function(value) {
                scales::percent(value, accuracy = 1)
            }
        ),
        mean_age = colDef(
            cell = function(value) {
                round(value, 1)
            }
        ),
        age_dist = colDef(
            cell = function(values) {
                sparkline(
                    values,
                    type = "box",
                    chartRangeMin = min(d$demo_age, na.rm = TRUE),
                    chartRangeMax = max(d$demo_age, na.rm = TRUE)
                )
            }
        )
    )
)
```

### Education

@fig-xp-client-edu shows the education level of client survey respondents by inclusion group.
At each level of education, the split between domestic and international education is shown in the fill colour. 

```{r}
#| label: fig-xp-client-edu
#| fig-cap: "Education Level of Client Survey Respondents by Inclusion Group"

tbl_educ <- d_long |> 
    filter(
        !is.na(demo_education),
        !is.na(demo_educ_domestic)
    ) |>
    group_by(inclusion_group = ig_short, demo_education, demo_educ_domestic) |>
    summarize(
        n = n(),
        .groups = "drop_last"
    ) |>
    group_by(inclusion_group) |>
    mutate(
        p = n / sum(n)
    )

tbl_educ |>
    ggplot(aes(p, demo_education, fill = demo_educ_domestic)) +
    geom_col(position = "stack") +
    facet_wrap(~inclusion_group, nrow = 2) +
    scale_fill_blueprint(discrete = TRUE, type = "bipolar", option = "blue_green") +
    theme_blueprint(base_size = 12, grid = "Xx") +
    scale_x_continuous(
        labels = scales::percent_format(accuracy = 1),
        limits = c(0, .5),
        expand = c(0, 0)
    )
```

@fig-xp-client-edu-ecdf is based on the same data as @fig-xp-client-edu, but rather than showing the proportion of respondents _at_ each level of education, it shows the proportion of respondents who have achieved _at least_ each level of education. 

```{r}
#| label: fig-xp-client-edu-ecdf
#| fig-cap: "Education Achievement of Client Survey Respondents by Inclusion Group"

tbl_educ_ecdf <- tbl_educ |>
    arrange(desc(demo_education)) |>
    group_by(inclusion_group, demo_educ_domestic) |>
    mutate(
        ecdf = cumsum(p)
    )


tbl_educ_ecdf |>
    ggplot(aes(ecdf, demo_education, fill = demo_educ_domestic)) +
    geom_col(position = "stack") +
    facet_wrap(~inclusion_group, nrow = 2) +
    scale_fill_blueprint(discrete = TRUE, type = "bipolar", option = "blue_green") +
    theme_blueprint(base_size = 12, grid = "Xx") +
    scale_x_continuous(
        labels = scales::percent_format(accuracy = 1),
        limits = c(0, 1),
        expand = c(0, 0)
    )
```

### Labour Force Status

@tbl-xp-client-lfs shows the labour force status of client survey respondents by inclusion group.
The employment rate is the proportion of respondents who are employed, the enrollment rate is the proportion of respondents who are enrolled in education, and the NEET rate is the proportion of respondents who are not in employment, education, or training.
The median annualized earnings are shown alongside the distribution of annualized earnings, visualized as a box plot for each inclusion group. 

:::{.callout-note}
## Sussy Data Alert!!

Self-reported employment rates and annualized earnings are _shockingly_ high for respondents who also self-reported having received payments from OW or ODSP _in the past two weeks_. 
:::

```{r}
#| label: tbl-xp-client-lfs
#| tbl-cap: "Labour Force Status of Client Survey Respondents by Inclusion Group"

tbl_emp <- d |>
    mutate(lfs_neet = !(lfs_employed | lfs_educ_enrolled)) |>
    pivot_longer(
        matches("^ig_"),
        names_to = "inclusion_group",
        values_to = "val"
    ) |>
    filter(val) |>
    mutate(inclusion_group = unlist(labs[inclusion_group])) |>
    group_by(inclusion_group) |>
    summarize(
        employment_rate = mean(lfs_employed, na.rm = TRUE),
        enrollment_rate = mean(lfs_educ_enrolled, na.rm = TRUE),
        neet_rate = mean(lfs_neet, na.rm = TRUE),
        median_annualized_earnings = median(job_annualized_earnings_total, na.rm = TRUE),
        annualized_earnings = list(na.omit(job_annualized_earnings_total))
    )

tbl_emp |>
    reactable(
        columns = list(
            employment_rate = colDef(
                cell = function(value) {
                    scales::percent(value, accuracy = 1)
                }
            ),
            enrollment_rate = colDef(
                cell = function(value) {
                    scales::percent(value, accuracy = 1)
                }
            ),
            neet_rate = colDef(
                cell = function(value) {
                    scales::percent(value, accuracy = 1)
                }
            ),
            median_annualized_earnings = colDef(
                format = colFormat(currency = "USD", separators = TRUE)
            ),
            annualized_earnings = colDef(
                cell = function(values) {
                    sparkline(
                        values,
                        type = "box",
                        chartRangeMin = 0,
                        chartRangeMax = 2.5e5
                    )
                }
            )
        )
    )
```

## Employment Services Client Characteristics

### Inclusion Group Representation

@tbl-xp-client-es-ig-rep shows the representation of inclusion groups among client survey respondents. 

```{r xp-igo-client-survey}
#| label: tbl-xp-client-es-ig-rep
#| tbl-cap: "Inclusion Group Representation Among ES Recipients in Client Survey"
#| warning: false
dplt_client_ig <- d_long_raw |>
    filter(engage_reached) |>
    group_by(inclusion_group_label) |>
    summarize(
        N = n(),
        n = sum(ig_member),
        p = n / N
    ) |>
    mutate(
        pn = glue::glue("{scales::percent(p, accuracy = 1)} ({n}/{N})")
    ) 

dplt_client_ig |>
    select(inclusion_group_label, sample_representation = pn) |>
    arrange(inclusion_group_label) |>
    gt() |>
    gtExtras::gt_theme_538() |>
    tab_source_note(
        source_note = dl_button(dplt_client_ig, "xp-client-igo")
    ) |> 
    cols_align(columns = c(sample_representation), align = "right")
```

@fig-xp-client-es-intersections shows the representation of each pair of inclusion groups among client survey respondents. Pairwise, the most common intersections we see are racialized newcomers, newcomers receiving social assistance, racialized francopohones, and francophone newcomers. 

```{r}
#| label: fig-xp-client-es-intersections
#| fig-cap: "Inclusion Group Intersections in Client Survey"
dplt_ig_int <- d_long_raw |>
    filter(engage_reached) |>
    filter(ig_short != "[Z]") |> 
    select(response_id, ig_x = ig_short, val_x = ig_member) |> 
    filter(!is.na(val_x)) %>%
    left_join(
        rename(., ig_y = ig_x, val_y = val_x),
        by = "response_id",
        relationship = "many-to-many"
    ) |>
    group_by(ig_x, ig_y) |>
    summarize(
        N = n(),
        n = sum(val_x * val_y),
        p = mean(val_x * val_y)
    )

dplt_ig_int |>
    ggplot(aes(ig_x, ig_y, fill = p)) +
    geom_tile() +
    geom_label(aes(label = scales::percent(p, accuracy = 1)), color = "black", fill = "grey90", size = 10) +
    scale_fill_viridis_c() +
    theme_blueprint(base_size = 14)
```

### Demographics

@tbl-xp-client-key-demos summarizes gender, parenthood, and age: the demographic characteristics included in the client survey but not reflected in the inclusion group indicator variables. 

```{r}
#| label: tbl-xp-client-key-demos
#| tbl-cap: "Age Distribution of Client Survey Respondents by Inclusion Group"
tbl_key_demos <- d_long |>
    filter(engage_reached) |>
    group_by(inclusion_group_label) |>
    summarize(
        p_woman_plus = mean(demo_gender != "Man", na.rm = TRUE),
        p_parent = mean(demo_parent, na.rm = TRUE),
        mean_age = mean(demo_age, na.rm = TRUE),
        age_dist = list(demo_age),
    ) |> 
    arrange(inclusion_group_label)

reactable(
    tbl_key_demos,
    columns = list(
        p_woman_plus = colDef(
            cell = function(value) {
                scales::percent(value, accuracy = 1)
            }
        ),
        p_parent = colDef(
            cell = function(value) {
                scales::percent(value, accuracy = 1)
            }
        ),
        mean_age = colDef(
            cell = function(value) {
                round(value, 1)
            }
        ),
        age_dist = colDef(
            cell = function(values) {
                sparkline(
                    values,
                    type = "box",
                    chartRangeMin = min(d$demo_age, na.rm = TRUE),
                    chartRangeMax = max(d$demo_age, na.rm = TRUE)
                )
            }
        )
    )
)
```

### Education

@fig-xp-client-es-edu shows the education level of client survey respondents by inclusion group.
At each level of education, the split between domestic and international education is shown in the fill colour. 

```{r}
#| label: fig-xp-client-es-edu
#| fig-cap: "Education Level of Client Survey Respondents by Inclusion Group"
tbl_educ <- d_long |>
    filter(
        !is.na(demo_education),
        !is.na(demo_educ_domestic),
        engage_reached
    ) |>
    mutate(
        demo_educ_domestic = fct_rev(demo_educ_domestic)
    ) |>
    group_by(inclusion_group_label = ig_short, demo_education, demo_educ_domestic) |>
    summarize(
        n = n(),
        .groups = "drop_last"
    ) |>
    group_by(inclusion_group_label) |>
    mutate(
        p = n / sum(n)
    )

tbl_educ |>
    ggplot(aes(p, demo_education, fill = demo_educ_domestic)) +
    geom_col(position = "stack") +
    facet_wrap(~inclusion_group_label, ncol = 2) +
    scale_fill_blueprint(discrete = TRUE, type = "bipolar", option = "blue_green") +
    theme_blueprint(base_size = 12, grid = "Xx") +
    scale_x_continuous(
        labels = scales::percent_format(accuracy = 1),
        limits = c(0, .5),
        expand = c(0, 0)
    )
```

@fig-xp-client-es-edu-ecdf is based on the same data as @fig-xp-client-es-edu, but rather than showing the proportion of respondents _at_ each level of education, it shows the proportion of respondents who have achieved _at least_ each level of education. 

```{r}
#| label: fig-xp-client-es-edu-ecdf
#| fig-cap: "Education Achievement of Client Survey Respondents by Inclusion Group"

tbl_educ_ecdf <- tbl_educ |>
    arrange(desc(demo_education)) |>
    group_by(inclusion_group_label, demo_educ_domestic) |>
    mutate(
        ecdf = cumsum(p)
    )


tbl_educ_ecdf |>
    ggplot(aes(ecdf, demo_education, fill = demo_educ_domestic)) +
    geom_col(position = "stack") +
    facet_wrap(~inclusion_group_label, ncol = 2) +
    scale_fill_blueprint(discrete = TRUE, type = "bipolar", option = "blue_green") +
    theme_blueprint(base_size = 12, grid = "Xx") +
    scale_x_continuous(
        labels = scales::percent_format(accuracy = 1),
        limits = c(0, 1),
        expand = c(0, 0)
    )
```

### Labour Force Status

@tbl-xp-client-es-lfs shows the labour force status of client survey respondents by inclusion group.
The employment rate is the proportion of respondents who are employed, the enrollment rate is the proportion of respondents who are enrolled in education, and the NEET rate is the proportion of respondents who are not in employment, education, or training.
The median annualized earnings are shown alongside the distribution of annualized earnings, visualized as a box plot for each inclusion group. 

```{r}
#| label: tbl-xp-client-es-lfs
#| tbl-cap: "Labour Force Status of Client Survey Respondents by Inclusion Group"

tbl_emp <- d_long |>
    mutate(lfs_neet = !(lfs_employed | lfs_educ_enrolled)) |>
    filter(engage_reached) |>
    group_by(inclusion_group_label) |>
    summarize(
        employment_rate = mean(lfs_employed, na.rm = TRUE),
        enrollment_rate = mean(lfs_educ_enrolled, na.rm = TRUE),
        neet_rate = mean(lfs_neet, na.rm = TRUE),
        median_annualized_earnings = median(job_annualized_earnings_total, na.rm = TRUE),
        annualized_earnings = list(na.omit(job_annualized_earnings_total))
    )

tbl_emp |>
    reactable(
        columns = list(
            employment_rate = colDef(
                cell = function(value) {
                    scales::percent(value, accuracy = 1)
                }
            ),
            enrollment_rate = colDef(
                cell = function(value) {
                    scales::percent(value, accuracy = 1)
                }
            ),
            neet_rate = colDef(
                cell = function(value) {
                    scales::percent(value, accuracy = 1)
                }
            ),
            median_annualized_earnings = colDef(
                format = colFormat(currency = "USD", separators = TRUE)
            ),
            annualized_earnings = colDef(
                cell = function(values) {
                    sparkline(
                        values,
                        type = "box",
                        chartRangeMin = 0,
                        chartRangeMax = 2.5e5
                    )
                }
            )
        )
    )
```

### Job Precarity

@tbl-xp-client-job-precarity summarizes the proportion of employed respondents who reported that their primary job was casual, seasonal, or temporary by inclusion group. The most common form of precarity reported is casual employment, making up 45% of primary jobs across the sample. Across each measure of precarity, social assistance recipients reported the highest rates.

```{r}
#| label: tbl-xp-client-job-precarity
#| tbl-cap: "Primary job precarity among employed respondents by inclusion group"

t_job_sat <- d_long |> 
    filter(lfs_employed) |> 
    pivot_longer(matches("^job_is_.*_primary"), names_to = "var", values_to = "val") |>
    group_by(ig_short, var) |> 
    summarize(
        p = mean(val, na.rm = TRUE)
    )

t_job_sat |> 
    pivot_wider(names_from = ig_short, values_from = p) |> 
    mutate(
        lab = case_when(
            var |> str_detect("casual") ~ "Casual", 
            var |> str_detect("seasonal") ~ "Seasonal", 
            var |> str_detect("temporary") ~ "Temporary"
        )
    ) |> 
    select(-var) |> 
    select(lab, everything()) |>  
    gt() |> 
    gtExtras::gt_theme_538() |> 
    gtExtras::gt_color_box(
        columns = c(matches("\\[")),
        domain = c(0, .9),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

### Employment Benefits

```{r}
#| label: tbl-xp-client-job-benefits
#| tbl-cap: "Access to benefits among employed respondents by inclusion group"

t_job_ben <- d_long |> 
    filter(lfs_employed) |>
    pivot_longer(matches("^job_benefits_.*_any"), names_to = "var", values_to = "val") |> 
    group_by(ig = ig_short, var) |> 
    summarize(p = mean(val)) 


t_job_ben |> 
    pivot_wider(names_from = ig, values_from = p) |> 
    mutate(
        lab = var |> 
            str_remove("job_benefits_") |> 
            str_remove("_any") |> 
            str_replace_all("_", " ") |> 
            str_replace("pto", "Paid Time Off") |> 
            str_replace("pension", "Retirement Savings Plan") |> 
            str_replace("disability", "Disability or Life Insurance") |> 
            str_to_title() 
    ) |> 
    select(-var) |> 
    select(lab, everything()) |>  
    gt() |> 
    gtExtras::gt_theme_538() |> 
    gtExtras::gt_color_box(
        columns = c(matches("\\[")),
        domain = c(0, .9),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```


### Job Satisfaction

@tbl-xp-client-job-sat summarizes net agreement[^net-agreement] with three statements concerning primary job[^primary-job] satisfaction among employed respondents by inclusion group. We see evidence of higher overall job satisfaction among social assistance recipients and youth. Social assistance recipients are particularly interesting here, as they were both the most optimistic group with respect to advancement opportunities whilst also being the most concerned about job precarity. Indigenous respondents reported roughly average levels of overall satisfaction, but were by quite a wide margin the least optimistic about advancement opportunities.

[^net-agreement]: Respondents were asked to indicate their level of agreement with each prompt on a five point scale ranging from "Strongly Disagree" to "Strongly Agree". Net agreement is calculated as the difference between the proportion of respondents who agreed or strongly agreed with the statement and the proportion who disagreed or strongly disagreed.
[^primary-job]: Respondents were asked to consider their primary job, meaning the job at which they typically spend the most time working, when responding to these questions.

```{r}
#| label: tbl-xp-client-job-sat
#| tbl-cap: "Primary job satisfaction among employed respondents by inclusion group"
t_job_sat <- d_long |> 
    filter(lfs_employed) |> 
    pivot_longer(matches("^job_sat_.*_primary"), names_to = "var", values_to = "val") |>
    group_by(ig = ig_short, var) |> 
    summarize(
        net_agree = mean(as.integer(val) < 3, na.rm = TRUE) - mean(as.integer(val) > 3, na.rm = TRUE)
    )

t_job_sat |> 
    pivot_wider(names_from = ig, values_from = net_agree) |> 
    mutate(
        lab = case_when(
            var |> str_detect("advance") ~ "I have opportunities to advance", 
            var |> str_detect("overall") ~ "I am satisfied with my job", 
            var |> str_detect("precarity") ~ "I worry about losing my job"
        )
    ) |> 
    select(-var) |> 
    select(lab, everything()) |>  
    gt() |> 
    gtExtras::gt_theme_538() |> 
    gtExtras::gt_color_box(
        columns = c(matches("\\[")),
        domain = c(-.7, .7),
        scale = 100,
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

### Job Precarity

@tbl-xp-es-client-job-precarity summarizes the proportion of employed respondents who reported that their primary job was casual, seasonal, or temporary by inclusion group. The most common form of precarity reported is casual employment, making up 45% of primary jobs across the sample. Across each measure of precarity, social assistance recipients reported the highest rates.

```{r}
#| label: tbl-xp-es-client-job-precarity
#| tbl-cap: "Primary job precarity among employed respondents by inclusion group"

t_job_sat <- d_long |> 
    filter(lfs_employed) |> 
    pivot_longer(matches("^job_is_.*_primary"), names_to = "var", values_to = "val") |>
    group_by(ig = ig_short, var) |> 
    summarize(
        p = mean(val, na.rm = TRUE)
    )

t_job_sat |> 
    pivot_wider(names_from = ig, values_from = p) |> 
    mutate(
        lab = case_when(
            var |> str_detect("casual") ~ "Casual", 
            var |> str_detect("seasonal") ~ "Seasonal", 
            var |> str_detect("temporary") ~ "Temporary"
        )
    ) |> 
    select(-var) |> 
    select(lab, everything()) |>  
    gt() |> 
    gtExtras::gt_theme_538() |> 
    gtExtras::gt_color_box(
        columns = c(matches("\\[")),
        domain = c(0, .9),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

## Experiences of Employment Services 

### Respondent Pathways Through Employment Services

```{r}
#| label: tbl-xp-client-pathways
#| tbl-cap: "Client Progress in Employment Services"
tbl_pathways <- d_long |>
    pivot_longer(
        matches("reached$"),
        names_pattern = "(.*)_reached$",
        names_to = "pathway_stage",
        values_to = "reached"
    ) |>
    mutate(
        pathway_stage = fct_relevel(
            pathway_stage,
            "engage",
            "explore",
            "progress",
            "start",
            "succeed"
        )
    ) |>
    arrange(
        pathway_stage
    ) |>
    group_by(inclusion_group, pathway_stage) |>
    summarize(
        p = mean(reached, na.rm = TRUE)
    ) |>
    mutate(
        inclusion_group = unlist(labs[inclusion_group])
    )


tbl_pathways |>
    pivot_wider(names_from = pathway_stage, values_from = p) |>
    arrange(inclusion_group) |>
    reactable(
        defaultColDef = colDef(
            format = colFormat(percent = T, digits = 0)
        )
    )

```

### Overall Satisfaction

@tbl-xp-client-nps summarizes the distribution Net Promoter Scores (NPS) within each inclusion group. As measured by NPS, respondent satisfaction with employment services is quite low. In each inclusion group and in the sample overall, the proportion of respondents in the 'Promoter' category is lower than the proportion in the 'Detractor' category. The upshot is that, within and around this set of respondents, we would expect word-of-mouth to be a net negative influence on demand for employment services. 

While this finding points to the existence of opportunities for improvement across the board, it is also worth noting that the distribution of NPS scores is not uniform across inclusion groups.
Indigenous respondents are by far the least likely to be employment services 'Promoters' and the most likely to be 'Detractors'. 
Individuals experiencing disability follow a similar pattern, though the difference from the sample averge (shown in the 'Total' row) is less pronounced. 

```{r}
#| label: tbl-xp-client-nps
#| tbl-cap: "Client Net Promoter Score by Inclusion Group"
d_sat <- d_long |> 
    filter(engage_reached) |> 
    mutate(
        es_promoter = ux_nps_nps_group %in% "Promoter", 
        es_detractor = ux_nps_nps_group %in% "Detractor",
        es_nps_marginal = 100 * (es_promoter - es_detractor),
    ) |> 
    arrange(
        ig_short
    ) |> 
    mutate(
        ig_short = fct_inorder(ig_short)
    )

t_es_ovr <- d_sat |> 
    group_by(ig = inclusion_group_label) |> 
    summarize(
        nps = mean(es_nps_marginal),
        promoter = mean(es_promoter), 
        detractor = mean(es_detractor), 
    )


t_es_ovr |>
    ungroup() |> 
    gt() |> 
    gtExtras::gt_theme_538() |> 
    gtExtras::gt_color_box(
        columns = c(promoter, detractor),
        domain = c(0, 1),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    ) |> 
    tab_style(
        style = cell_fill(color = "gray95"), 
        locations = cells_body(
            columns = nps
        )
    ) |> 
    fmt_number(columns = nps, decimals = 0) |> 
    tab_footnote(
        "NPS is calculated as the difference between the proportion of respondents who are promoters and the proportion who are detractors."
    )
```

@tbl-xp-client-nps-intersections shows NPS for members of each pair of inclusion groups. 

```{r}
#| label: tbl-xp-client-nps-intersections
#| tbl-cap: "Client Net Promoter Score by Inclusion Group Intersection"
d_sat_xy <- d_sat |> 
    select(response_id, ig_x = ig_short, es_nps_marginal) |> 
    left_join(
        d_sat |> select(response_id, ig_y = ig_short), 
        by = "response_id",
        relationship = "many-to-many"
    ) |> 
    filter(as.integer(ig_x) > as.integer(ig_y))
    

t_es_ovr_int <- d_sat_xy |> 
    group_by(ig_x, ig_y) |> 
    summarize(
        nps = mean(es_nps_marginal), 
        .groups = "drop"
    )

t_es_ovr_int |> 
    pivot_wider(names_from = ig_y, values_from = nps) |> 
    gt(rowname_col = "ig_x") |> 
    gtExtras::gt_theme_538() |>
    fmt_missing() |> 
    fmt_number(
        columns = c(-ig_x), 
        decimals = 0, 
        force_sign = TRUE
    ) |> 
    tab_header(
        title = "Net Promoter Score by Inclusion Group Intersection"
    )
```

### Holistic Reflections

@tbl-xp-client-holistic-sum summarizes the percentage of employment services clients who responded "Always" to a series of questions about their experiences with employment services. 

```{r}
#| label: tbl-xp-client-holistic-sum
#| tbl-cap: "Summary of Client Holistic Reflections on Employment Services"
tbl_holistic_sum <- d_long |>
    filter(engage_reached) |>
    pivot_longer(
        matches("^ux_journey"),
        names_to = "var",
        values_to = "val"
    ) |>
    mutate(
        lab = unlist(labs[var]) |> str_remove("^.*? - ")
    ) |>
    filter(
        !is.na(val)
    ) |>
    group_by(
        ig_short,
        lab
    ) |>
    summarize(
        p = mean(val %in% c("Always")),
        .groups = "drop_last"
    )

tbl_holistic_sum |>
    pivot_wider(
        names_from = ig_short,
        values_from = p
    ) |>
    group_by(lab) |>
    gt(groupname_col = "lab") |>
    gtExtras::gt_theme_538() |>
    # fmt_percent(columns = 2:6, decimals = 0) |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_row_groups(groups = everything())
    ) |>
    gtExtras::gt_color_box(
        columns = c(-lab),
        domain = c(0, .5),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

@tbl-xp-client-holistic shows the full distribution of responses to holistic reflection questions within each inclusion group.
The questions are designed to capture the respondent's overall experience with employment services. 
The experiences about which they inquire can be broadly thought of as 'table stakes', meaning that they represent a kind of foundational, minimum level of service quality. 
It feels uncontroversial to suggest that employment services clients should always feel like they know what is happing with their cases, that each activity is productive, and that they are given a safe space in which to discuss their needs. 
However, among the respondents in this sample, these experiences unfortunately comprise a minority of the total. 


```{r}
#| label: tbl-xp-client-holistic
#| tbl-cap: "Client Holistic Reflections on Employment Services"

tbl_holistic <- d_long |>
    filter(engage_reached) |>
    pivot_longer(
        matches("^ux_journey"),
        names_to = "var",
        values_to = "val"
    ) |>
    mutate(
        lab = unlist(labs[var]) |> str_remove("^.*? - ")
    ) |>
    filter(
        !is.na(val)
    ) |>
    group_by(
        inclusion_group_label,
        lab,
        val
    ) |>
    summarize(
        n = n(),
        .groups = "drop_last"
    ) |>
    mutate(
        p = n / sum(n)
    )

tbl_holistic |>
    select(-n) |>
    pivot_wider(
        names_from = val,
        values_from = p
    ) |>
    group_by(lab) |>
    gt(groupname_col = "lab", rowname_col = "inclusion_group_label") |>
    gtExtras::gt_theme_538() |>
    # fmt_percent(columns = 2:6, decimals = 0) |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_row_groups(groups = everything())
    ) |>
    gtExtras::gt_color_box(
        columns = 2:6,
        domain = c(0, .6),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )

```

### Reflections on Career Exploration

@tbl-xp-client-explore-sum reports net agreement with a pair of statements about the experience of career exploration within employment services.

```{r}
#| label: tbl-xp-client-explore-sum
#| tbl-cap: "Client Reflections on Career Exploration (Net Agreement)"

tbl_explore_sum <- d_long |>
    filter(explore_reached) |>
    pivot_longer(
        matches("^explore_reflections"),
        names_to = "var",
        values_to = "val"
    ) |>
    mutate(
        lab = unlist(labs[var]) |> str_remove("^.*? - ")
    ) |>
    filter(!is.na(val)) |>
    group_by(inclusion_group_label = ig_short, lab) |>
    summarize(
        p = mean(as.integer(val) < 3, na.rm = TRUE) - mean(as.integer(val) > 3, na.rm = TRUE),
        .groups = "drop_last"
    )

tbl_explore_sum |>
    pivot_wider(
        names_from = inclusion_group_label,
        values_from = p
    ) |>
    group_by(lab) |>
    gt(groupname_col = "lab") |>
    gtExtras::gt_theme_538() |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_row_groups(groups = everything())
    ) |>
    gtExtras::gt_color_box(
        columns = everything(),
        domain = c(.4, .8),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

@tbl-xp-client-explore summarizes the full distribution of responses to questions about respondent experiences of career exploration as part of their employment services journies.
Here, we see evidence that newcomers, youth, and _especially_ Indigenous clients are less likely to feel that their goals and needs are consistently understood by the employment services system. 

```{r}
#| label: tbl-xp-client-explore
#| tbl-cap: "Client Reflections on Career Exploration"

tbl_explore <- d_long |>
    filter(explore_reached) |>
    pivot_longer(
        matches("^explore_reflections"),
        names_to = "var",
        values_to = "val"
    ) |>
    mutate(
        lab = unlist(labs[var]) |> str_remove("^.*? - ")
    ) |>
    filter(!is.na(val)) |>
    group_by(inclusion_group_label, lab, val) |>
    summarize(
        n = n(),
        .groups = "drop_last"
    ) |>
    mutate(
        p = n / sum(n)
    )

tbl_explore |>
    select(-n) |>
    pivot_wider(
        names_from = val,
        values_from = p
    ) |>
    group_by(lab) |>
    gt(groupname_col = "lab", rowname_col = "inclusion_group_label") |>
    gtExtras::gt_theme_538() |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_row_groups(groups = everything())
    ) |>
    gtExtras::gt_color_box(
        columns = 2:7,
        domain = c(0, .6),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

### Reflections on Making Progress

@tbl-xp-client-progress summarizes the distribution of responses to questions about respondent experiences of codesigning and making progress in their plans for employment. 
These figures echo the trends observed above: newcomers, youth, and Indigenous clients disproprotionately feel that the employment services system does not communicate with them effectively, nor does it understand the goals and needs they express.
Naturally, members of the same set of groups are less likely to report confidence in the effectiveness of the plan, and less likely to feel that it is responsive to their needs. 

```{r}
#| label: tbl-xp-client-progress
#| tbl-cap: "Client Reflections on Making Progress"

tbl_progress <- d_long |>
    filter(progress_reached) |>
    pivot_longer(
        matches("^progress_reflections"),
        names_to = "var",
        values_to = "val"
    ) |>
    mutate(
        lab = unlist(labs[var]) |> str_remove("^.*? - ")
    ) |>
    filter(!is.na(val)) |>
    group_by(inclusion_group_label, lab, val) |>
    summarize(
        n = n(),
        .groups = "drop_last"
    ) |>
    mutate(
        p = n / sum(n)
    )

tbl_progress |>
    select(-n) |>
    pivot_wider(
        names_from = val,
        values_from = p
    ) |>
    group_by(lab) |>
    gt(groupname_col = "lab", rowname_col = "inclusion_group_label") |>
    gtExtras::gt_theme_538() |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_row_groups(groups = everything())
    ) |>
    gtExtras::gt_color_box(
        columns = 2:7,
        domain = c(0, .6),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

### Reflections on Starting Employment

@tbl-xp-client-start summarizes the distribution of responses to questions about respondent experiences of starting employment as part of their employment services journies.
Kind of seeing the same old saw at this point: newcomers, youth, and Indigenous clients are unsurprisingly less confident in their ability to succeed and less likely to attribute their attainment of employment to the employment services they received. 

```{r}
#| label: tbl-xp-client-start
#| tbl-cap: "Client Reflections on Starting Employment"

tbl_start <- d_long |>
    filter(start_reached) |>
    pivot_longer(
        matches("^start_reflections"),
        names_to = "var",
        values_to = "val"
    ) |>
    mutate(
        lab = unlist(labs[var]) |> str_remove("^.*? - ")
    ) |>
    filter(!is.na(val)) |>
    group_by(inclusion_group_label, lab, val) |>
    summarize(
        n = n(),
        .groups = "drop_last"
    ) |>
    mutate(
        p = n / sum(n)
    )

tbl_start |>
    select(-n) |>
    pivot_wider(
        names_from = val,
        values_from = p
    ) |>
    group_by(lab) |>
    gt(groupname_col = "lab", rowname_col = "inclusion_group_label") |>
    gtExtras::gt_theme_538() |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_row_groups(groups = everything())
    ) |>
    gtExtras::gt_color_box(
        columns = 2:7,
        domain = c(0, .6),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```

### Reflections on Support in Employment

@tbl-xp-client-support summarizes the distribution of responses to questions about respondent experiences of support from employment services once they secured employment.

```{r}
#| label: tbl-xp-client-support
#| tbl-cap: "Client Reflections on Support in Employment"

tbl_succeed <- d_long |>
    filter(succeed_reached) |>
    pivot_longer(
        matches("^succeed_reflections"),
        names_to = "var",
        values_to = "val"
    ) |>
    mutate(
        lab = unlist(labs[var]) |> str_remove("^.*? - ")
    ) |>
    filter(!is.na(val)) |>
    group_by(inclusion_group_label, lab, val) |>
    summarize(
        n = n(),
        .groups = "drop_last"
    ) |>
    mutate(
        p = n / sum(n)
    )

tbl_succeed |>
    select(-n) |>
    pivot_wider(
        names_from = val,
        values_from = p
    ) |>
    group_by(lab) |>
    gt(groupname_col = "lab", rowname_col = "inclusion_group_label") |>
    gtExtras::gt_theme_538() |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_row_groups(groups = everything())
    ) |>
    gtExtras::gt_color_box(
        columns = 2:7,
        domain = c(0, .6),
        scale = 100,
        suffix = "%",
        palette = c("#0000FF", "#f2f2f2", "#ff4500")
    )
```