# Stakeholders


```{r}
#| label: xp-stake-pkg
#| cache: false
library(tidyverse)
library(labelled)
library(gt)
library(gtExtras)
library(reactable)
library(sparkline)
library(bptheme)
library(bpscales)
source(here::here("R/zzz.R"))
source(here::here("R/extract.R"))
source(here::here("R/transform.R"))
```


```{r}
#| label: xp-stake-data
#| cache: true

d0 <- load_qx_surveys() 

d <- clean_stakeholder(d0)
labs <- stakeholder_var_labels(d0)
```


## Respondent Information

@tbl-xp-stakeholder-ig reports, for each inclusion group, the number of respondents who indicated that their organization serves that group and the number of organizations that set of respondents represents. 

```{r}
#| label: tbl-xp-stakeholder-ig
#| tbl-cap: "N by inclusion group"
d |> 
  unnest(ig_loop) |> 
  filter(ig_served) |> 
  group_by(ig_label) |> 
  summarize(
    n = n(), 
    n_org = n_distinct(id_org_short)
  ) |> 
  arrange(desc(n_org)) |> 
  gt() |> 
  gtExtras::gt_theme_538() |> 
  cols_align(columns = 1, align = "left")
```

@tbl-xp-stakeholder-org reports the number and percentage of respondents by home organization. For each organization, columns [D] to [S-D] indicate whether any of the respondents from that organization served each inclusion group. 

```{r}
#| label: tbl-xp-stakeholder-org
#| tbl-cap: "N by respondent organization"
d |> 
  unnest(ig_loop) |> 
  group_by(ig_short, id_org_clean) |> 
  summarize(
    n = n(),
    ig_served = any(ig_served), 
    .groups = "drop_last"
  ) |>
  mutate(
    p = n / sum(n)
  ) |> 
  pivot_wider(
    names_from = ig_short, 
    values_from = ig_served
  ) |> 
  arrange(desc(n)) |> 
  reactable(
    defaultColDef = colDef(
      cell = function(v) {
        if (is.logical(v) && v) {
          "\u2714\ufe0f" 
        } else if (is.logical(v)) {
          "\u274c" 
        } else {
          v
        }
      }
    ),
    columns = list(
      id_org_clean = colDef(
        header = "Organization"
      ),
      p = colDef(
        cell = function(v) {
          scales::percent(v, accuracy = 1)
        }
      )
    )
  )
```

@tbl-xp-stakeholder-roles reports the number of respondents who indicated that their organizations serve each inclusion group, by the organization's primary role.

```{r}
#| label: tbl-xp-stakeholder-roles
#| tbl-cap: "N by role"
d |> 
  unnest(ig_loop) |> 
  filter(ig_served) |> 
  group_by(
    ig_short, 
    org_role_primary
  ) |>
  summarize(
    n = n()
  ) |> 
  pivot_wider(names_from = ig_short, values_from = n) |> 
  group_by(org_role_primary) |> 
  gt() |> 
  gt_theme_538() |> 
  fmt_missing()
```

## Serving Inclusion Groups

@tbl-xp-stakeholder-barriers reports the distribution of responses to questions about the barriers that negatively impact the employment prospects of each inclusion group.

```{r}
#| label: tbl-xp-stakeholder-barriers
#| tbl-cap: "Staff-rated barriers (% responding 'High Impact')"
d |> 
  unnest(ig_loop) |> 
  filter(ig_served) |> 
  select(response_id, ig_short, matches("ig_barriers")) |> 
  pivot_longer(
    cols = matches("ig_barriers"), 
    names_to = "var",
    names_transform = list(
      var = function(x) {
        labs$ig_insights[x] |> 
          stringr::str_extract("(?<=ers - ).*?$") |> 
          stringr::str_replace("\\[Field-1\\]", "[X]")
      }
    ),
    values_to = "val"
  ) |>
  mutate(
    high_impact = val == "High Impact"
  ) |> 
  group_by(
    ig_short, 
    var
  ) |> 
  summarize(
    net_agree = mean(high_impact, na.rm = TRUE)
  ) |> 
  pivot_wider(names_from = ig_short, values_from = net_agree) |> 
  group_by(var) |> 
  gt() |> 
  gt_theme_538() |> 
  fmt_percent(
    columns = c(-var), 
    decimals = 0
  ) |> 
  tab_header(
    title = "Based on your experiences working with [X], to what degree do each of the following barriers negatively impact their employment prospects?"
  )
```

## Success Factors

We asked respondents about the importance of various factors in the employment success of each inclusion group. Responses were collected on a four point scale with the following options: 

1. "Absolutely Necessary"
2. "Very Important"
3. "Somewhat Important"
4. "Not Important"

@tbl-xp-stakeholder-job-factors reports, for each factor and inclusion group, the percentage of respondents who rated the factor as "Absolutely Necessary" or "Very Important".

```{r}
#| label: tbl-xp-stakeholder-job-factors
#| tbl-cap: "Staff-rated job factors (% responding 'Absolutely Necessary' or 'Very Important')"
d |> 
  unnest(ig_loop) |> 
  filter(ig_served) |> 
  select(response_id, ig_short, matches("ig_success_factors")) |> 
  pivot_longer(
    cols = matches("ig_success_factors"), 
    names_to = "var",
    names_transform = list(
      var = function(x) {
        labs$ig_insights[x] |> 
          stringr::str_extract("(?<=ers - ).*?$") |> 
          stringr::str_replace("\\[Field-1\\]", "[X]")
      }
    ),
    values_to = "val"
  ) |>
  mutate(
    x = as.integer(val) < 3
  ) |> 
  group_by(
    ig_short, 
    var
  ) |> 
  summarize(
    x = mean(x, na.rm = TRUE)
  ) |> 
  pivot_wider(names_from = ig_short, values_from = x) |> 
  group_by(var) |> 
  gt() |> 
  gt_theme_538() |> 
  fmt_percent(
    columns = c(-var), 
    decimals = 0
  ) |> 
  tab_header(
    title = "Based on your experiences working with [X], how important are each of the following job features to their sustainable employment?"
  )
```

Using the same scale, we also asked respondents about the importance of various social supports in the employment success of each inclusion group.
@tbl-xp-stakeholder-social-supports reports the percentage of respondents who rated each social support as "Absolutely Necessary" or "Very Important".

```{r}
#| label: tbl-xp-stakeholder-social-supports
#| tbl-cap: "Stakeholder-rated social factors (% responding 'Absolutely Necessary' or 'Very Important')"

d |> 
  unnest(ig_loop) |> 
  filter(ig_served) |> 
  select(response_id, ig_short, matches("ig_social_supports")) |> 
  pivot_longer(
    cols = matches("ig_social_supports"), 
    names_to = "var",
    names_transform = list(
      var = function(x) {
        labs$ig_insights[x] |> 
          stringr::str_extract("(?<=ers - ).*?$") |> 
          stringr::str_replace("\\[Field-1\\]", "[X]")
      }
    ),
    values_to = "val"
  ) |>
  mutate(
    x = as.integer(val) < 3
  ) |> 
  group_by(
    ig_short, 
    var
  ) |> 
  summarize(
    x = mean(x, na.rm = TRUE)
  ) |> 
  pivot_wider(names_from = ig_short, values_from = x) |> 
  group_by(var) |> 
  gt() |> 
  gt_theme_538() |> 
  fmt_percent(
    columns = c(-var), 
    decimals = 0
  ) |> 
  tab_header(
    title = "Based on your experiences working with [X], how important do each of the following social supports tend to be for their sustainable employment?"
  )
```

