# Staff Survey


```{r}
#| label: xp-staff-require
#| output: false
#| require: true
#| cache: false
library(tidyverse)
library(labelled)
library(gt)
library(gtExtras)
library(reactable)
library(sparkline)
library(bptheme)
library(bpscales)
source(here::here("R/zzz.R"))
source(here::here("R/extract.R"))
source(here::here("R/transform.R"))
```

```{r}
#| label: xp-staff-data

d0 <- load_qx_surveys()
d <- d0 |> clean_staff()
labs <- staff_var_labels(d0)
```

## Respondent Information

@tbl-xp-staff-ig reports, for each inclusion group, the number of respondents who indicated that their organization serves that group and the number of organizations that set of respondents represents. 

Respondents to the staff survey most commonly reported serving the Newcomer, Ontario Works, and Racialized inclusion groups. Staff at Francophone-serving organizations are the least represented in the sample. 

```{r}
#| label: tbl-xp-staff-ig
#| tbl-cap: "N by inclusion group"
d |>
    unnest(ig_loop) |>
    filter(ig_served) |>
    group_by(ig_label) |>
    summarize(
        n = n(),
        n_org = n_distinct(id_org_short)
    ) |>
    arrange(desc(n_org)) |>
    gt() |>
    gtExtras::gt_theme_538() |>
    cols_align(columns = 1, align = "left")
```

@tbl-xp-staff-org reports the number and percentage of respondents by home organization. For each organization, columns [D] to [S-D] indicate whether any of the respondents from that organization "typically serve" members of each inclusion group. 

The organizations represented in our sample tend to be generalists with respect to the inclusion groups they typically serve. 
Of the 24 organizations, staff respondents from seven indicated that they typically serve members of all 8 inclusion groups. 
Fred Victor was the only organization whose staff didn't select multiple inclusion groups, though the inclusion group they _did_ select is OW recipients. 
The diversity of that group suggests that FV's staff may have interpreted the question differently than staff at other organizations. 


```{r}
#| label: tbl-xp-staff-org
#| tbl-cap: "N by respondent organization"
d |>
    unnest(ig_loop) |>
    group_by(ig_short, id_org_clean) |>
    summarize(
        n = n(),
        ig_served = any(ig_served),
        .groups = "drop_last"
    ) |>
    mutate(
        p = n / sum(n)
    ) |>
    pivot_wider(
        names_from = ig_short,
        values_from = ig_served
    ) |>
    arrange(desc(n)) |>
    reactable(
        defaultColDef = colDef(
            cell = function(v) {
                if (is.logical(v) && v) {
                    "\u2714\ufe0f"
                } else if (is.logical(v)) {
                    "\u274c"
                } else {
                    v
                }
            }
        ),
        columns = list(
            id_org_clean = colDef(
                header = "Organization"
            ),
            p = colDef(
                cell = function(v) {
                    scales::percent(v, accuracy = 1)
                }
            )
        )
    )
```

@tbl-xp-staff-roles reports the number of respondents who indicated that they serve each inclusion group, by role.
At least across the generalized functional role descriptions about which we inquired, respondents tended to identify themselves as generalists, 
performing a variety of functions throughout their clients' employment services journeys. 

```{r}
#| label: tbl-xp-staff-roles
#| tbl-cap: "N by role"
d |>
    unnest(ig_loop) |>
    pivot_longer(matches("^id_role_\\d$"), names_to = "id_role_var", values_to = "has_role") |>
    filter(has_role, ig_served) |>
    mutate(id_role_label = labs$id_role[id_role_var]) |>
    group_by(ig_short, id_role_label) |>
    summarize(
        n = n()
    ) |>
    pivot_wider(names_from = ig_short, values_from = n) |>
    group_by(id_role_label) |>
    gt() |>
    gt_theme_538()
```

## Serving Inclusion Groups

@tbl-xp-staff-challenge reports, for each inclusion group, the percentage of eligible respondents who selected each of the provided challenges when asked about the biggest challenge they face serving clients in that group. 
Connecting clients with employment and maintaining client engagement seem like the most challenging aspects of providing employment services. 
Indigenous clients seem more challenging to recruit than others. 
Staff serving francophones found assessing needs and developing action plans especially difficult


```{r}
#| label: tbl-xp-staff-challenge
#| tbl-cap: "Biggest challenge"
d |>
    unnest(ig_loop) |>
    filter(ig_served, !is.na(ig_challenges)) |>
    group_by(ig_short, ig_challenges) |>
    summarize(n = n(), .groups = "drop_last") |>
    mutate(p = n / sum(n)) |>
    select(-n) |>
    group_by(ig_short) |>
    arrange(ig_short, desc(p)) |>
    gt(row_group_as_column = TRUE) |>
    gt_theme_538() |>
    tab_header(
        title = "Based on your experiences working with [X], which aspect of your role do you find the most challenging?"
    ) |>
    fmt_percent(
        columns = c(-ig_challenges),
        decimals = 0
    ) |>
    fmt_missing()


```

@tbl-xp-staff-support reports the net agreement with statements about the efficacy and preparedness of staff to serve each inclusion group.

```{r}
#| label: tbl-xp-staff-support
#| tbl-cap: "Staff-rated efficacy and preparedness (net agreement)"

d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_support",
        svy = "staff",
        title = "Based on your experiences working with [X], how much do you agree with each of the following statements?",
        subtitle = "net agreement [% agree - % disagree]",
        val_transform = function(x) {
            100 * ((as.integer(x) < 3) - (as.integer(x) > 3))
        }
    )
```

@tbl-xp-staff-support-full summarizes the full distribution of responses to the same set of survey questions. 

```{r}
#| label: tbl-xp-staff-support-full
#| tbl-cap: "Staff-rated efficacy and preparedness (full distribution)"

d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_support",
        svy = "staff",
        title = "Based on your experiences working with [X], how much do you agree with each of the following statements?",
        subtitle = "full distribution"
    )
```


@tbl-xp-staff-barriers reports the distribution of responses to questions about the barriers that negatively impact the employment prospects of each inclusion group.

```{r}
#| label: tbl-xp-staff-barriers
#| tbl-cap: "Staff-rated barriers (% responding 'High Impact')"
d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_barriers",
        svy = "staff",
        val_transform = function(x) x == "High Impact",
        title = "Based on your experiences working with [X], to what degree do each of the following barriers negatively impact their employment prospects?",
        subtitle = "% responding 'High Impact'"
    )
```

@tbl-xp-staff-barriers-full summarizes the full distribution of responses to the same set of survey questions.

```{r}
#| label: tbl-xp-staff-barriers-full
#| tbl-cap: "Staff-rated barriers (full distribution)"

d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_barriers",
        svy = "staff",
        title = "Based on your experiences working with [X], to what degree do each of the following barriers negatively impact their employment prospects?",
        subtitle = "full distribution"
    )
```


## Success Factors

We asked respondents about the importance of various factors in the employment success of each inclusion group. Responses were collected on a four point scale with the following options: 

1. "Absolutely Necessary"
2. "Very Important"
3. "Somewhat Important"
4. "Not Important"

@tbl-xp-staff-job-factors reports, for each factor and inclusion group, the percentage of respondents who rated the factor as "Absolutely Necessary" or "Very Important".

```{r}
#| label: tbl-xp-staff-job-factors
#| tbl-cap: "Staff-rated job factors (% responding 'Absolutely Necessary' or 'Very Important')"
d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_success_factors",
        svy = "staff",
        val_transform = function(x) as.integer(x) < 3,
        title = "Based on your experiences working with [X], how important are each of the following job features to their sustainable employment?",
        subtitle = "% responding 'Absolutely Necessary' or 'Very Important'"
    )
```


@tbl-xp-staff-job-factors-full summarizes the full distribution of responses to the same set of survey questions. 

```{r}
#| label: tbl-xp-staff-job-factors-full
#| tbl-cap: "Staff-rated job factors (full distributdion)"

d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_success_factors",
        svy = "staff",
        title = "Based on your experiences working with [X], how important are each of the following job features to their sustainable employment?",
        subtitle = "full distribution"
    )
```


Using the same scale, we also asked respondents about the importance of various social supports in the employment success of each inclusion group.
@tbl-xp-staff-social-supports reports the percentage of respondents who rated each social support as "Absolutely Necessary" or "Very Important".

```{r}
#| label: tbl-xp-staff-social-supports
#| tbl-cap: "Staff-rated social factors (% responding 'Absolutely Necessary' or 'Very Important')"

d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_social_supports",
        svy = "staff",
        val_transform = function(x) as.integer(x) < 3,
        title = "Based on your experiences working with [X], how important do each of the following social supports tend to be for their sustainable employment?",
        subtitle = "% responding 'Absolutely Necessary' or 'Very Important'"
    )
```

@tbl-xp-staff-social-supports-full summarizes the full distribution of responses to the same set of survey questions.


```{r}
#| label: tbl-xp-staff-social-supports-full
#| tbl-cap: "Staff-rated social factors (full distribution)"

d |>
    st_ig_tab(
        palette = "viridis",
        l = labs,
        var_pattern = "ig_social_supports",
        svy = "staff",
        title = "Based on your experiences working with [X], how important do each of the following social supports tend to be for their sustainable employment?",
        subtitle = "full distribution"
    )
```