# Stakeholder Survey


```{r}
#| label: xp-stake-pkg
#| cache: false
#| output: false
#| warning: false
library(tidyverse)
library(labelled)
library(gt)
library(gtExtras)
library(reactable)
library(sparkline)
library(bptheme)
library(bpscales)
source(here::here("R/zzz.R"))
source(here::here("R/extract.R"))
source(here::here("R/transform.R"))
```


```{r}
#| label: xp-stake-data
#| cache: true

d0 <- load_qx_surveys()

d <- clean_stakeholder(d0)
labs <- stakeholder_var_labels(d0)
```


## Respondent Information

@tbl-xp-stakeholder-ig reports, for each inclusion group, the number of respondents who indicated that their organization serves that group and the number of organizations that set of respondents represents. 

```{r}
#| label: tbl-xp-stakeholder-ig
#| tbl-cap: "N by inclusion group"
d |>
    unnest(ig_loop) |>
    filter(ig_served) |>
    group_by(ig_label) |>
    summarize(
        n = n(),
        n_org = n_distinct(id_org_short)
    ) |>
    arrange(desc(n_org)) |>
    gt() |>
    gtExtras::gt_theme_538() |>
    cols_align(columns = 1, align = "left")
```

@tbl-xp-stakeholder-org reports the number and percentage of respondents by home organization. For each organization, columns [D] to [S-D] indicate whether any of the respondents from that organization served each inclusion group. 

```{r}
#| label: tbl-xp-stakeholder-org
#| tbl-cap: "N by respondent organization"
d |>
    unnest(ig_loop) |>
    group_by(ig_short, id_org_clean) |>
    summarize(
        n = n(),
        ig_served = any(ig_served),
        .groups = "drop_last"
    ) |>
    mutate(
        p = n / sum(n)
    ) |>
    pivot_wider(
        names_from = ig_short,
        values_from = ig_served
    ) |>
    arrange(desc(n)) |>
    reactable(
        defaultColDef = colDef(
            cell = function(v) {
                if (is.logical(v) && v) {
                    "\u2714\ufe0f"
                } else if (is.logical(v)) {
                    "\u274c"
                } else {
                    v
                }
            }
        ),
        columns = list(
            id_org_clean = colDef(
                header = "Organization"
            ),
            p = colDef(
                cell = function(v) {
                    scales::percent(v, accuracy = 1)
                }
            )
        )
    )
```

@tbl-xp-stakeholder-roles reports the number of respondents who indicated that their organizations serve each inclusion group, by the organization's primary role.

```{r}
#| label: tbl-xp-stakeholder-roles
#| tbl-cap: "N by role"
d |>
    unnest(ig_loop) |>
    filter(ig_served) |>
    group_by(
        ig_short,
        org_role_primary
    ) |>
    summarize(
        n = n()
    ) |>
    pivot_wider(names_from = ig_short, values_from = n) |>
    group_by(org_role_primary) |>
    gt() |>
    gt_theme_538() |>
    fmt_missing()
```

## Serving Inclusion Groups

@tbl-xp-stakeholder-barriers reports the distribution of responses to questions about the barriers that negatively impact the employment prospects of each inclusion group.

```{r}
#| label: tbl-xp-stakeholder-barriers
#| tbl-cap: "Stakeholder-rated barriers (% responding 'High Impact')"
d |>
    st_ig_tab(
        l = labs,
        var_pattern = "ig_barriers",
        val_transform = function(x) x == "High Impact",
        svy = "stakeholder",
        title = "Based on your experiences working with [X], to what degree do each of the following barriers negatively impact their employment prospects? (% responding 'High Impact')"
    )
```

@tbl-xp-stakeholder-barriers-full summarizes the full distribution of responses to the same set of survey questions.

```{r}
#| label: tbl-xp-stakeholder-barriers-full
#| tbl-cap: "Stakeholder-rated barriers (full distribution)"

d |>
    st_ig_tab(
        l = labs,
        var_pattern = "ig_barriers",
        svy = "stakeholder",
        title = "Based on your experiences working with [X], to what degree do each of the following barriers negatively impact their employment prospects? (full distribution)"
    )
```

## Success Factors

We asked respondents about the importance of various factors in the employment success of each inclusion group. Responses were collected on a four point scale with the following options: 

1. "Absolutely Necessary"
2. "Very Important"
3. "Somewhat Important"
4. "Not Important"

@tbl-xp-stakeholder-job-factors reports, for each factor and inclusion group, the percentage of respondents who rated the factor as "Absolutely Necessary" or "Very Important".

```{r}
#| label: tbl-xp-stakeholder-job-factors
#| tbl-cap: "Staff-rated job factors (% responding 'Absolutely Necessary' or 'Very Important')"
d |>
    st_ig_tab(
        l = labs,
        var_pattern = "ig_success_factors",
        val_transform = function(x) x %in% c("Absolutely Necessary", "Very Important"),
        svy = "stakeholder",
        title = "Based on your experiences working with [X], how important are each of the following job features to their sustainable employment?",
        subtitle = "% responding 'Absolutely Necessary' or 'Very Important'"
    )
```

@tbl-xp-stakeholder-job-factors-full summarizes the full distribution of responses to the same set of survey questions. 

```{r}
#| label: tbl-xp-stakeholder-job-factors-full
#| tbl-cap: "Stakeholder-rated job factors (full distributdion)"

d |>
    st_ig_tab(
        l = labs,
        var_pattern = "ig_success_factors",
        svy = "stakeholder",
        title = "Based on your experiences working with [X], how important are each of the following job features to their sustainable employment?",
        subtitle = "full distribution"
    )
```

Using the same scale, we also asked respondents about the importance of various social supports in the employment success of each inclusion group.
@tbl-xp-stakeholder-social-supports reports the percentage of respondents who rated each social support as "Absolutely Necessary" or "Very Important".

```{r}
#| label: tbl-xp-stakeholder-social-supports
#| tbl-cap: "Stakeholder-rated social factors (% responding 'Absolutely Necessary' or 'Very Important')"

d |>
    st_ig_tab(
        l = labs,
        var_pattern = "ig_social_supports",
        val_transform = function(x) x %in% c("Absolutely Necessary", "Very Important"),
        svy = "stakeholder",
        title = "Based on your experiences working with [X], how important do each of the following social supports tend to be for their sustainable employment?",
        subtitle = "% responding 'Absolutely Necessary' or 'Very Important'"
    )
```

@tbl-xp-stakeholder-social-supports-full summarizes the full distribution of responses to the same set of survey questions.

```{r}
#| label: tbl-xp-stakeholder-social-supports-full
#| tbl-cap: "Stakeholder-rated social factors (full distribution)"

d |>
    st_ig_tab(
        l = labs,
        var_pattern = "ig_social_supports",
        svy = "stakeholder",
        title = "Based on your experiences working with [X], how important do each of the following social supports tend to be for their sustainable employment?",
        subtitle = "full distribution"
    )
```

